\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{times}
\usepackage{cite}
\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage{caption}
%this is a comment
\title{The Memo}
\author{Jesse Chick\\
\and Benjamin Martin\\
\and Keenan Johnson\\
\and Nickoli Londura\\
\and Jiaji Sun}




\begin{document}
\maketitle
\tableofcontents

\section{Contributors and ONIDs}
\par
LINK TO THE GITHUB REPO AT THE CORRECT BRANCH: 

\begin{itemize}
	\item Jesse Chick $\sim$ chickj
	\item Benjamin Martin $\sim$ martinb3
	\item Keenan Johnson $\sim$ johnsoke
	\item Nickoli Londura $\sim$ londuran
	\item Jiaji Sun $\sim$ sunji
\end{itemize}

\section{}

\section{}


\section{Sequence Diagrams}


\section{Meeting Report}
\par
On this week we have met four times on campus. Including three times in library and one meeting after class. \\

\par
On our first meeting on Wednesday. We met everyone still in the library. we separate our third phase of the project to every group member. Jesse Chick is working on class diagrams and prepare for the presentation. Benjamin Martin is working on design patterns. Keenan Johnson is working on packages. He is preparing presentation also. Nickoli Londura is working on exceptions and handling. Jiaji Sun is working on meeting report. On this meeting, we have tried four different architectures. However, we found our first version architecture is much better than other solution. It’s the best solution for this project. The running time is shortest one and it is the easiest one to maintain. On the end of this meeting, we basically settle down our final version of UML class diagram. We decided to work on packages and design patterns for next meeting. \\


\cite{rubtut}

\bibliography{myref}
\bibliographystyle{plain}

\end{document}
